Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
More algorithm

In lines ?? we use the reasoning from section ?? to eliminate infeasible initial values from the
domains. We do not use iterated label filtering ?? cite to recalculate neighbourhood degree
sequences if any vertices are not present in any target domain after construction: preliminary
experiments indicated that this happened very rarely.

@@

We begin by trying to infer domain deletions. The ?? function looks for domains which contains
either only a single value, or only wildcards---we call such a domain ``effectively-unit''. If such
a domain $D_v$ exists, we eliminate its value from every other domain, and then propagate adjacency:
for each domain corresponding to a vertex adjacent to $v$, we eliminate any value from its domain
which is not adjacent to $v$ (treating wildcards as being adjacent to all vertices). If a domain
wipeout occurs, we return failure.

?? Supplemental graphs. These are also used for eliminating infeasible values.

If no effectively-unit domains remain, we attempt stronger propagation for the all-different
constraint. Our ?? function is the bit-parallel propagator taken from
\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? which
guarantees generalised arc consistency. ?? a bit more on how it works. It can easily be seen that
this propagator will always find Hall sets or failed Hall sets of size zero or one, but it may miss
larger sets. This propagation could create new effectively-unit domains; if so, we loop.

?? This technique allows us to retain the bit-parallel all different propagator used in the original
algorithm.

@@

?? As well as the modifications to solve $k$-less and induced problems, we have made two
simplifications: we do not use conflict-directed backjumping, and in preliminary experiments, these
techniques were not beneficial for $k > 0$.

To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
using path reasoning on complement graphs, but this is expensive to calculate and provides little
benefit in practice on the instances we considered.  We also do not strip isolated vertices as
cite?? did, as this is not a valid simplification in the induced case.

>>>>

In lines ?? we use the reasoning from \cref{section:degreefiltering} to eliminate infeasible initial
values from the domains. We do not use iterated label filtering \citep{constraints10} to recalculate
neighbourhood degree sequences if any vertices are not present in any target domain after
construction: preliminary experiments indicated that this happened very rarely on our instances.

@@

We begin by trying to infer domain deletions. The $\FuncSty{propagate}$ function looks for domains
which contains either only a single value, or only wildcards---we call such a domain
``effectively-unit''. If such a domain $D_v$ exists, we eliminate its value from every other domain,
and then propagate adjacency: for each domain corresponding to a vertex adjacent to $v$, we
eliminate any value from its domain which is not adjacent to $v$ (treating wildcards as being
adjacent to all vertices). If a domain wipeout occurs, we return failure.

?? Describe supplemental graphs. These are also used for eliminating infeasible values.

If no effectively-unit domains remain, we attempt stronger propagation for the all-different
constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? cite
which guarantees generalised arc consistency. Because we use multiple wildcard values, we do not
need to modify the algorithm to allow a single wildcard value to be used more than once. ?? a bit
more on how it works?. It can easily be seen that this propagator will always find Hall sets or
failed Hall sets of size zero or one, but it may miss larger sets. This propagation could create new
effectively-unit domains; if so, we loop.

@@

To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
using path reasoning on complement graphs, but this is expensive to calculate and provides little
benefit in practice on the instances we considered.  We also do not strip isolated vertices as the
original algorithm did, as this is not a valid simplification in the induced case, and we do not use
conflict-directed backjumping as in our experiments it had very little effect for $k > 0$.
